A sparse grid that is fully nested and well suited for local adaptivity, which
we requested previous, can be constructed using the (one-dimensional)
Newton--Cotes rule \cite{klimke2006, ma2009}. For each level, the rule is merely
a set of equidistant nodes on an interval, which is $[0, 1]$ in our case.

\begin{remark}
Equidistant nodes are known to perform poorly when the interpolating functions
are polynomials (Runge's phenomenon). However, it is not a concern for us as our
basis functions are not exposed to this problem.
\end{remark}

The rule comes in two flavors: closed and open. The only difference between the
two is that the former includes the endpoints, that is, 0 and 1, while the
latter does not. Now, at the end of \sref{smolyak-algorithm}, we postulated that
the assumption in \eref{tensor-exactness} was needed to proceed. The closed rule
satisfies this assumption while the open one violates it close to the boundaries
of the interval. However, as noted in \cite{klimke2006}, the open Newton--Cotes
rule is a viable option since it performs well in practice. We were able to
achieve better results using the open rule, and, therefore, we have decided to
present it in the paper.

\input{include/assets/figures/rule}
The open Newton--Cotes rule of level $i \in \natural$ is
\begin{equation} \elab{newton-cotes-grid}
  \X_i = \left\{ x_{ij} = \frac{j + 1}{\n_i + 1}: j \in \index_i \right\}
\end{equation}
where $\index_i = \left\{ 0, \dots, \n_i - 1 \right\}$ with $\n_i = 2^{i + 1} -
1$. The first three levels of the rule are depicted in \fref{rule}. It can be
seen that the number of nodes (in one dimension) grows as 1, 3, 7, 15, 31, and
so on, and the rule is fully nested. In multiple dimensions, the nodes are
formed as shown in \eref{collocation-nodes}.

Figure~\ref{fig:rule} also illustrates a refinement procedure suitable for this
grid. The arrows emerging from a node connect the node with its next-level
neighbors. The number of such neighbors is two in one dimension and $2 \nin$ in
general. Formally, for a pair $(\vi, \vj)$, the neighbor pairs are
\[
  \left\{ \Big( (i_1, \dots, i_k + 1, \dots, i_\nin), (j_1, \dots, 2 j_k + c, \dots j_\nin) \Big) \right\}_{k, c}
\]
for $k = 1, \dots, \nin$ and $c \in \{ 0, 2 \}$. Whenever a node is chosen for
refinement, some or all of its neighbors can be added to the interpolant. One
possible strategy is to include all $2 \nin$ neighbors, which is what we shall
do.

\begin{remark}
It is important to note that an arbitrary set of nodes identified by some pairs
$\{ (\vi_k, \vj_k) \}_k$ does not necessarily correspond to a valid
construction. In order to have a valid construction, the multi-indices $\{ \vi_k
\}_k$ should satisfy a so-called admissibility condition \cite{klimke2006}. The
condition is diligently satisfied when the refinement is undertaken level by
level following neighbor connections, which is what we do.
\end{remark}

First of all, looking at \eref{smolyak-hierarchical}, it is not clear what the
interpolation level $\l$ should be in order to achieve a certain accuracy level.
When should we stop?
