Consider a multiprocessor system composed of two major components: a platform
and an application. The platform consists of a set of heterogeneous processing
elements $\procs = \{ 1, 2, \dots, \np \}$ and is equipped with a thermal
package. The application is given as a set of tasks $\tasks = \{ 1, 2, \dots,
\nt \}$. In what follows, the system will be denoted by $(\procs, \tasks)$.

In this work, the mapping of the application onto the platform is assumed to be
fixed, and it is given by a vector $\mapping = (m_i)_{i = 1}^{\nt}$ wherein $m_i
\in \procs$ is the index of the processing element that the $i$th task is
assigned to. Likewise, the power consumption of the tasks is assumed to be
fixed, and it is given by a vector $\power = (p_i)_{i = 1}^{\nt}$ wherein $p_i$
is the power of the $i$th task. Note that the boundaries of a task have not been
specified, and one can perform modeling at the level of granularity that makes
the most sense for a particular problem.

Each task is ascribed two variables: one is the beginning of the task's
execution time interval, and the other is the duration of this interval. For the
$i$th task, denote the two variables by $\b_i$ and $\d_i$, respectively, and let
$\vb = (\b_i)_{i=1}^{\nt}$ and $\vd = (\d_i)_{i=1}^{\nt}$.

The tuple $(\vb, \vd)$ becomes completely known after the application has been
scheduled and executed. We shall refer to the overall procedure as a scheduling
procedure and denote it by $\schedule$. The procedure depends on a set of
parameters that are uncertain at the design stage. We model such uncertain
parameters as a random vector $\vu = (\u_i)_{i = 1}^\nu \sim \distribution_\vu$.
For a given $\vu$, $\schedule$ is assumed to be purely deterministic. We shall
denote the relation between $(\vb, \vd)$, $\schedule$, and $\vu$ by
$\schedule(\vu) = (\vb, \vd)$.

It is important to note that the dependency of the system's schedule on the
random vector $\vu$ inevitably implies that the quantities dependent on the
schedule---for example, the end-to-end delay and power and temperature profiles
of the system---are inevitable uncertain for the designer as well.

We pursue the following major objectives:
\begin{itemize}

\item {\bfseries Objective~1.} Develop a framework for performance analysis of
  the system $(\procs, \tasks)$ with the given mapping $\mapping$, power
  consumption $\power$, and scheduling procedure $\schedule$ such that the
  uncertainty due the parameters $\vu$---affecting the timing characteristics of
  the system comprised in the tuple $(\vb, \vd)$---is taken into consideration.

\end{itemize}
