In this section, we present the interpolation algorithm that forms the core of
the proposed framework for probabilistic analysis of electronic systems. The
algorithm is based on the work in \cite{jakeman2012, klimke2006, ma2009}, and it
features a sparse-grid structure, hierarchical construction, and hybrid
adaptivity. The benefits of these features are interconnected and can be
summarized as follows: the ability to mitigate the curse of dimensionality and,
thereby, tackle multidimensional problems; the ability to perform gradual
refinement of the approximation with a natural error control; and the ability to
make the refinement fine-grained and, hence, gain further efficiency.

Let $\f$ be a function that we would like to approximate. The function is
assumed to be in $\continuous([0, 1]^\nin)$, the space of continuous functions
in the unit hypercube $[0, 1]^\nin$. The assumption is a formality, and the
interpolation algorithm discussed in \sref{implementation} can be applied to
functions with finite discontinuities as well, which is actually the case in the
example given in \fref{motivation}. Furthermore, the domain $[0, 1]^\nin$ is
merely standardization rather than a restriction.

In what follows, we shall gradually construct an efficient interpolant for $\f$.
Efficiency here refers to the number of collocation nodes required to achieve a
certain accuracy level.

\subsection{Tensor Product} \slab{tensor-product}
\input{include/interpolation/tensor-product}

\subsection{Smolyak Algorithm} \slab{smolyak-algorithm}
\input{include/interpolation/smolyak-algorithm}

\subsection{Collocation Nodes} \slab{collocation-nodes}
\input{include/interpolation/collocation-nodes}

\subsection{Basis Functions} \slab{basis-functions}
\input{include/interpolation/basis-functions}

\subsection{Adaptivity} \slab{adaptivity}
\input{include/interpolation/adaptivity}

To summarize, we have obtained an efficient algorithm for adaptive hierarchical
interpolation in multiple dimensions. The main equation is \eref{approximation}
where $\surplus$, $\vx_{\vi\vj}$, and $\e_{\vi\vj}$ are the ones given in
\sref{smolyak-algorithm}, \sref{collocation-nodes}, and \sref{basis-functions},
respectively, and the interpolation procedure is undertaken according to the
rules given in \sref{adaptivity}. In the next subsection, we shall discuss the
algorithmic structure of our interpolation.

\subsection{Implementation} \slab{implementation}
\input{include/interpolation/implementation}

To recapitulate, in this section, we have presented the key component of the
proposed framework for probabilistic analysis of electronic systems: an
efficient approach to multidimensional interpolation. The interpolation
technique is based on the Smolyak algorithm, which enables the interpolation to
be performed in an adaptive hierarchical manner, highly beneficial for practical
computations. The overall technique has been consolidated in \aref{construct}
and \aref{evaluate}.
