A sparse grid that is fully nested and well suited for local adaptivity, which
we required previous, can be constructed using the (one-dimensional)
Newton--Cotes rule \cite{klimke2006, ma2009}. For each level, the rule is merely
a set of nodes evenly distributed on an interval, which is $[0, 1]$ in our case.

\begin{remark}
Equidistant nodes are known to perform purely when the interpolating functions
are chosen to be polynomials (Runge's phenomenon). However, it is not a concern
for us as our basis functions do not have this problem.
\end{remark}

The rule comes in two flavors: closed and open. The only difference between the
two is that the former includes the endpoints, that is, 0 and 1, while the
latter does not. Now, at the end of \sref{smolyak-algorithm}, we postulated that
the assumption in \eref{tensor-exactness} was needed to proceed. The closed rule
satisfies this assumption while the open one violates it close to the boundaries
of the interval. However, according to our numerical experiments and as noted in
\cite{klimke2006}, the open Newton--Cotes rule is a viable option as it performs
well in practice.

Despite the minor concern noted above, we have decided to present the open
Newton--Cotes rule in the paper as it is a better match for the transformation
in \eref{transformation}. The problem with 0 and 1 is rather technical and is as
follows. The inverse of the Gaussian distribution function, $\Phi^{-1}$, maps 0
and 1 to $-\infty$ and $+\infty$, respectively; the resulting vector then gets
multiplied by a matrix, as shown in \eref{transformation}. Since certain
algebraic operations with infinite values are undefined---for instance, $0.42
\times (+\infty) + 0.27 \times (-\infty)$---this particular transformation in
\eref{transformation} might need to be adjusted, which we would like to avoid by
choosing a rule without the endpoints.

\input{include/assets/rule}
The open Newton--Cotes rule of level $i \in \natural$ is
\[
  \X^i = \left\{ x^i_j = \frac{j + 1}{\n_i + 1}: j \in \index(i) \right\}
\]
where $\index(i) = \left\{ 0, 1, \dots, \n_i - 1 \right\}$ with $\n_i = 2^{i +
1} - 1$. The first three levels of the rule are depicted in \fref{rule}. It can
be seen that the number of nodes (in one dimension) grows as 1, 3, 7, 15, 31,
and so on, and the rule is fully nested. 
